Nix for Polyglot, Reproducible Data Science Workflows

### 2025-10-21 paper.qmd
Update paper.qmd

[Nix]{.pkg} is a powerful, cross-platform package manager designed for installing 
and building software in a fully reproducible and reliable manner. Unlike traditional 
package managers, [Nix]{.pkg} emphasizes immutable infrastructure and a functional
approach, which significantly enhances the consistency of computational environments.
As of writing, the primary Nix package collection, `nixpkgs`, provides access to over 
120,000 packages, including nearly all of CRAN and Bioconductor. 
This extensive coverage allows users to install not only [R]{.proglang} itself but 
also all its required packages and system-level dependencies for any given project.

>>>>

[Nix]{.pkg} is a powerful, cross-platform package manager designed for installing 
and building software in a fully reproducible and reliable manner. Unlike traditional 
package managers, [Nix]{.pkg} emphasizes immutable infrastructure and a functional
approach, which significantly enhances the consistency of computational environments.
As of writing, the primary Nix package collection, `nixpkgs`, provides access to over 
120,000 packages, including nearly all of CRAN and Bioconductor, making it the largest,
and among the most up-to-date package repository according to Repology:

![nixpkgs is the largest and among the most up-to-date packages repository](repology.png){#fig-repology}

This extensive coverage allows users to install not only [R]{.proglang} itself but 
also all its required packages and system-level dependencies for any given project.
